Effectiveness of Instant Feedback on Developer Navigation Practices

### 2013-08-29 paper_id1.tex
Added bibliography

\section{Introduction}

@@

Developing the study with the available tooling means that we follow steps as follows.
1. define the practice we wish to measure compliance with
2. Develop a mapping of the practice to actions that are captured by the blaze tool from the IDE
3. Weight the actions according to their importance to the practice and assign points to the actions in the configuration file
4. Develop the intervention method
5. Determine the phases and length of the phase in the study according to baseline, intervention, and continuous feedback
6. Select participants to deploy
7. Define a pre-study questionnaire if one is necessary to collect associated information
8. Define a post-study questionnaire if necessary to collect post study information
9. Communicate with the participants about the study
10. Execute the study and report results

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

>>>>

\section{Introduction}
%update
Deploying these techniques requires communicating and motivating developers to use them.  Murphy-Hill and colleagues  \cite{wbsnipes:Hill2011Peer} show that developers can effectively learn about new tools from their peers by watching them work and through recommendations, yet this happens very rarely, in part because developers rarely work on the same computer at the same time.  This personal connection limits the knowledge transfer to the co-located circle of colleagues connected with the early adopters.  
%update
Finding a way to automate the communication of technique recommendations between developers enhances deployment of best practices in a globally distributed software development organization.   
%PF the following sounds redundant
To best match the peer recommendation scenario described above, the method should mimic the personal recommendation model while rewarding successful adopters.

@@

Developing the study with the available tooling means that we follow steps as follows.
1. Define the practice we wish to measure compliance with
2. Develop a mapping of the practice to actions that are captured by the blaze tool from the IDE
3. Weight the actions according to their importance to the practice and assign points to the actions in the configuration file
4. Develop the intervention method
5. Determine the phases and length of the phase in the study according to baseline, intervention, and continuous feedback
6. Select participants to deploy
7. Define a pre-study questionnaire if one is necessary to collect associated information
8. Define a post-study questionnaire if necessary to collect post study information
9. Communicate with the participants about the study
10. Execute the study and report results

\subsection{Setup the practice}
Selecting a practice to study involves defining specific characteristics of the practice and how capturing actions in Visual Studio relates to the practice.  In this study we selected the structured navigation practice shown by Robillard et. al. as correlated with effective program maintenance \cite{wbsnipes:Robillard2004How} .

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\balance
\bibliography{paper_id1}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command% \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}
